% Documentation for the uofsthesis-cs class is given in uofsthesis-cs.dvi
% 
% It is recommended that you read the CGSR thesis preparation
% guidelines before proceeding.
% They can be found at http://www.usask.ca/cgsr/thesis/index.htm
\documentclass{uofsthesis-cs}
% \usepackage[margin=2.5cm]{geometry}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{physics}
\usepackage{float, subcaption, graphicx}
\usepackage[font=small,labelfont=bf]{caption}
% \usepackage{hyperref} % comment this in school template
% \usepackage{setspace}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{tikz, tikzscale, pgfplots}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{codestyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
\lstset{style=codestyle}
% \onehalfspacing

\theoremstyle{plain}
\newtheorem{proposition}{Proposition}

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\newtheorem{theorem}{Theorem}

\newtheorem*{remark}{Remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FRONTMATTER - In this section, specify information to be used to
% typeset the thesis frontmatter.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% THESIS TITLE
% Specify the title. Set the capitalization how you want it.
\title{Spectral Stability of Plasma Flows In the Magnetic Nozzle}
% AUTHOR'S NAME
% Your name goes here.
\author{Hunt Feng}

% DEGREE SOUGHT.  
% Use \MSc or \PhD here
\degree{\MSc}

% THESIS DEFENCE DATE
% Should be month year, e.g. July 2004
\defencedate{August 2024}


% NAME OF ACADEMIC UNIT
%
% The following two commands allow you to specify the academic unit you belong to.
% This will appear on the title page as
% ``<academic unit> of <department>''.
% So if you are in the division of biomedical engineering you would need to do:
% \department{Physics and Engineering Physics}
% \academicunit{Division}
%
% The default is ``Department of Computer Science'' if these commands
% are not given.
%
% If you are in a discipline other than Computer Science, uncomment the following line and
% specify your discipline/department.  Default is 'Computer Science'.
\department{Physics and Engineering Physics}

% If you are not in a department, but say, a division, uncomment the following line.
% \academicunit{Put the type of academic unit you belong to here, e.g. Division, College}


% PERMISSION TO USE ADDRESS
%
% If you are not in Comptuer Science you will want to change the
% address on the Permission to Use page.  This is done using the
% \ptuaddress{}.  Example:
%
\ptuaddress{Head of the Department of Physics and Engineering Physics\\
116 Science Place\\
University of Saskatchewan\\
Saskatoon, Saskatchewan\\
Canada\\
S7N 5E2
}

% ABSTRACT
\abstract{
In this thesis, spectral stability of plasmas is understood as an eigenvalue problem of linearized plasma equations describing time dynamics near some equilibrium state. Presence of eigenvalues with positive imaginary part would indicate the instability when small fluctuations will grow (typically exponentially) in time. A particular focus is the stability of plasma with stationary flows, in particular, flows in the magnetic nozzle. Magnetic nozzle, or magnetic mirror configurations, with converging-diverging magnetic field are used to accelerate plasma in plasma propulsion systems (magnetic Laval nozzle) and in fusion devices aiming to confine plasma and reach controlled thermonuclear fusion. We consider the linear stability of plasma flows under different boundary conditions. The linearized plasma equations are discretized and spectral stability  problem is reduced to a polynomial eigenvalue problem. We found that the subsonic and supersonic flows are stable for Dirichlet boundary conditions. The subsonic flow is stable for the mixed (fixed-open) boundary conditions, but the supersonic flow is unstable. We show that different spectral methods, i.e. spectral collocation and spectral Galerkin methods, agree. Phenomena of spectral pollution resulting in spurious unstable modes is discussed. By studying the convergence of different modes, we successfully eliminated the spurious modes. The stability problem of the transonic velocity profile has an additional difficulty due to the singularity at the sonic point, i.e. at the point when the flow velocity is equal to the local sound velocity. At this point, the coefficient in front of the highest derivative of the differential eigenvalue equation becomes zero. In this case, the direct application of the spectral  methods is problematic. To solve this problem, we solve the equation near the singularity by the Frobenius method and then use the regular solution with  the shooting method to find the eigenvalues. We find that the transonic accelerating velocity profile is stable.
}

% THESIS ACKNOWLEDGEMENTS -- This can be free-form.
\acknowledgements{
  I would like to express my gratitude to my supervisor, Prof. Andrei Smolyakov, for his continuous support, motivation and guidance throughout my work on this thesis. I am thankful to be able to learn from him and be supervised by him. I am also thankful to Prof. Adam Bourassa for his help.
  I extend my heartfelt thanks to my family and especially my wife Alice. Her continuous support has made my master's program a joyful journey. I also grateful to my little baby boy, Johnathan, who gives me courage and inspiration every day.
  Lastly, I want to thank all my good friends in Saskatoon. The time we spent discussing physics, movies, musics and French made Saskatoon feel like home. 
}

% THESIS DEDICATION -- Also free-form.  If you don't want a dedication, comment out the following
% line.
% \dedication{This is the thesis dedication (optional)}

% LIST OF ABBREVIATIONS - Sample  
% If you don't want a list of abbreviations, comment the following 4 lines.
% \loa{
% \abbrev{SCUBA}{Self Contained Underwater Breathing Apparatus\hfill}
% \abbrev{LOF}{List of Figures}
% \abbrev{LOT}{List of Tables}
% }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% END OF FRONTMATTER SECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
% Typeset the title page
\maketitle

% Typeset the frontmatter.  
\frontmatter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIRST CHAPTER OF THESIS BEGINS HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{introduction}
\input{fluid-equations}
\input{eigenvalue-problem}
\input{spectral-method}
\input{singular-perturbation}
\input{discussion}

% Since thesis chapters are very long and there are a lot of them, it is recommended
% that you put each chapter in a separate .tex file and \input each one of them
% in order.  For example:
%
% \input chap1.tex
% \input chap2.tex
% ...
%
% The \input command inserts contents of the specified file at the point of the command.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SUBSEQUENT CHAPTERS (or \input's)  GO HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%






%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The Bibliograpy should go here. BEFORE appendices!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% Typeset the Bibliography.  The bibliography style used is "plain".
% Optionally, you can specify the bibliography style to use:
% \uofsbibliography[stylename]{yourbibfile}

\uofsbibliography[plain]{references}
% comment the following in production
\bibliographystyle{plain}
\bibliography{references}
\nocite{*}

% If you are not using bibtex, comment the line above and uncomment
% the line below.  
%Follow the line below with a thebibliography environmentand bibitems.  
% Note: use of bibtex is usually the preferred method.

%\uofsbibliographynobibtex


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% APPENDICES
%
% Any chapters appearing after the \appendix command get numbered with
% capital letters starting with appendix 'A'.
% New chapters from here on will be called 'Appendix A', 'Appendix B'
% as opposed to 'Chapter 1', 'Chapter 2', etc.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Activate thesis appendix mode.
\uofsappendix

% Put appendix chapters in the appendices environment so that they appear correcty
% in the table of contents.  You can use \input's here as well.
\begin{appendices}
	\input{verification-of-analytical-solutions.tex}
\end{appendices}

\end{document}
